Stateless Model Checking with Data-Race Preemption Points

### 2015-10-20 pldi-16/di.tex
It lets us avoid thrashing in Quicksand.

With a limited CPU budget, we must avoid running tests likely to time out.
When a MC instance reports an ETA too high,
% TODO: find some way to point out that heuristic factor is needed because the estimates are imperfect
%(greater than some heuristic factor times the time remaining),
we compare other yet-untested PP sets to find another job more likely to complete in time.
This algorithm is the heart of Iterative Deepening; we list it in Algorithm~\ref{alg:shouldworkblock}\footnote{
Though its worst-case performance is $O(mn)$ in the number of pending and suspended jobs,
in practice the non-constant portion runs very infrequently
and is negligible compared to the exponentially-sized state spaces.}.
The algorithm takes into account... TODO

% TODO: should work block / find work algorthm here

@@

%Note that Algorithm~\ref{alg:shouldworkblock} accounts for the bizarre possibility that given two jobs,
%%$j_1,j_2$,
%\GetPPSet{$j_1$} $\subset$ \GetPPSet{$j_2$}
%but
%\GetETA{$j_1$} $>$ \GetETA{$j_2$}.
%This can arise because the estimation gets more accurate over time \cite{estimation},
%and one job perhaps ran much longer before suspending.
%% In such scenarios,
%We heuristically assume the smaller job's ETA is more accurate,

>>>>

With a limited CPU budget, we must avoid running tests likely to time out.
When a MC instance reports an ETA too high,
we compare other yet-untested PP sets to find another job more likely to complete in time.
This algorithm is the heart of Iterative Deepening; we list it in Algorithm~\ref{alg:shouldworkblock}\footnote{
Though its worst-case performance is $O(mn)$ in the number of pending and suspended jobs,
in practice the non-constant portion runs very infrequently
and is negligible compared to the exponentially-sized state spaces.}.
%

Our method's main feature is that it understands that if \GetPPSet{$j_1$} $\subset$ \GetPPSet{$j_2$},
and $j_1$ is suspended, $j_2$'s state space is guaranteed to be strictly larger, so $j_2$ would take at least as long.
Hence we should avoid testing $j_2$ unless further time spent on $j_1$ reveals that it might finish in time after all.
%
We also account for the inherent inaccuracy of ETA estimates.
Line 1 heuristically scales up the time remaining to avoid suspending jobs too aggressively
when their ETAs are actually overestimates.
Lines 12-14 account for the
%bizarre
possibility that among two suspended jobs,
%given two jobs,
%%$j_1,j_2$,
\GetPPSet{$j_1$} $\subset$ \GetPPSet{$j_2$}
but
\GetETA{$j_1$} $>$ \GetETA{$j_2$}.
This can arise because estimates tend to get more accurate over time,
and $j_1$ perhaps ran much longer before suspending.
% In such scenarios,
We heuristically assume the smaller job's ETA is more accurate
to avoid repeatedly resuming larger jobs very briefly while their ETAs only become worse
(it lets us avoid thrashing in \quicksand),

@@
